---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

> Disclaimer: this is experimental, use deliberately and with caution.

# craneur

The goal of craneur is to provide an easy way to Create your own "R Archive Network". 

## Install {craneur}

```{r eval = FALSE}
install.packages("craneur", repos = "https://colinfay.me", type = "source")
```

## Why would you use `{craneur}`?

Creating your own R archive repository can be useful for: 

+ Not depending on GitHub for your dev packages 
+ Internal uses in your company, lab, university... 
+ Because you're a nerd and find it cool

## How does it work? 

A R archive repo is a location where you can download R packages with the `install.packages` function. 

This location is composed of, roughly: 

+ a `PACKAGES` file
+ the `tar.gz` of your packages

These elements should be put inside a `src/contrib` folder. 

Once you've installed that, you can do : 

```{r eval=FALSE}
install.packages("pkg", repos = "my_repos.com", type = "source")
```

For example :

```{r eval=FALSE}
install.packages("attempt", repos = "https://colinfay.me", type = "source")
```

## Here comes `{craneur}`

`craneur` provides a user-friendly API for creating this skeleton : `PACKAGES` file, tar.gz, and a minimal `index.html`.

```{r}
library(craneur)
colin <- Craneur$new("Colin")
colin$add_package("../craneur_0.0.0.9000.tar.gz")
colin$add_package("../jekyllthat_0.0.0.9000.tar.gz")
colin$add_package("../tidystringdist_0.1.2.tar.gz")
colin$add_package("../attempt_0.2.1.tar.gz")
colin$add_package("../rpinterest_0.4.0.tar.gz")
colin$add_package("../rgeoapi_1.2.0.tar.gz")
colin$add_package("../proustr_0.3.0.9000.tar.gz")
colin$add_package("../languagelayeR_1.2.3.tar.gz")
colin$add_package("../fryingpane_0.0.0.9000.tar.gz")
colin$add_package("../dockerfiler_0.1.1.tar.gz")
colin$add_package("../devaddins_0.0.0.9000.tar.gz")
colin
```

Create it:

```{r eval = FALSE}
colin$write(path = ".")
```

This creates a "src/contrib" folder, and copies all the tar.gz into this folder. 

For a bulk import, you can : 

```{r}
colin <- Craneur$new("Colin")
lapply(list.files("../", pattern = "tar.gz", full.names = TRUE), function(x) colin$add_package(x))
```

### Put on your sever

You can now put the full "src/contrib" folder onto your server. 

For example, if I put "src/contrib" at the root of "https://colinfay.me", here the index: https://colinfay.me/src/contrib/ 

You can now install with : 

```{r eval = FALSE}
install.packages("craneur", repos = "https://colinfay.me", type = "source")
install.packages("jekyllthat", repos = "https://colinfay.me", type = "source")
install.packages("tidystringdist", repos = "https://colinfay.me", type = "source")
install.packages("attempt", repos = "https://colinfay.me", type = "source")
install.packages("rpinterest", repos = "https://colinfay.me", type = "source")
install.packages("rgeoapi", repos = "https://colinfay.me", type = "source")
install.packages("proustr", repos = "https://colinfay.me", type = "source")
install.packages("languagelayeR", repos = "https://colinfay.me", type = "source")
install.packages("fryingpane", repos = "https://colinfay.me", type = "source")
install.packages("dockerfiler", repos = "https://colinfay.me", type = "source")
install.packages("devaddins", repos = "https://colinfay.me", type = "source")
```

## Personnalise home page

You can rewrite your index.html by reknitting the index.Rmd you'll find in the directory. 

## Prior work 

See also: 

+ `{drat}`: [https://github.com/eddelbuettel/drat](https://github.com/eddelbuettel/drat)
+ `{cranlike}`: [https://github.com/r-hub/cranlike](https://github.com/r-hub/cranlike)
+ `{packrat}`: [https://github.com/rstudio/packrat](https://github.com/rstudio/packrat)

## CoC

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
